\appendix

\chapter{AI Image Generation Model Prompts}
    \textbf{Used AI Model:} Midjourney 7 Standart
    
    \textbf{Style Prompt:}
    \begin{itemize}
        \item Style: Cinematic realism, 35mm film grain texture, desaturated color palette 
        \item Lighting: Natural overcast lighting with cool temperature bias (5000K-5500K) 
        \item Color Grading: Teal and orange color scheme, lifted shadows, crushed blacks 
        \item Aspect Ratio: 16:9 widescreen format Camera: Medium format aesthetic, shallow depth of field where applicable.
    \end{itemize}

    \textbf{Image 1 Prompt:} Wide establishing shot, camera capturing from behind of the young man in dark green fur-lined parka, face not visible, sitting alone on wooden bench placed on the pedestrian lane of massive steel truss bridge architecture with asphalt double lane, overcast gray sky with dramatic cloud formations, murder of crows perched on bridge cables and flying overhead, cold mist rising from water below, 35mm film aesthetic, desaturated colors, shallow depth of field on character, industrial gothic atmosphere.

    \textbf{Image 2 Prompt:} Medium shot, sleek dark sedan approaching from left frame, passenger window rolled down showing pitch-black interior, driver's silhouette barely visible, young man in green parka visible in background on bench, steel bridge structure overhead, overcast lighting, cinematic composition, teal-orange color grading, film grain texture.

    \textbf{Image 3 Prompt:} Close-up profile shot, young man in green parka leaning into dark car interior, car door open, one foot inside vehicle, hesitant body language, dramatic chiaroscuro lighting, dark interior contrasting with overcast exterior, steel bridge girders visible above, handheld camera feel, shallow focus on character, moody atmosphere.

    \textbf{Image 4 Prompt:} Close-up, analog speedometer dashboard with red needle pointing to high RPM zone 5-6, needle in motion blur, reflection of rushing bridge scenery in chrome bezel, dramatic lighting from dashboard illumination, film grain, high contrast, sense of urgency and speed.

    \textbf{Image 5 Prompt:} Wide dynamic shot, dark sedan airborne mid-fall from metal constructed bridge, river surface below, dramatic composition, bridge structure silhouetted against gray sky, car captured at moment of weightlessness, cinematic lighting, epic scale showing height and danger, film grain aesthetic.

    \textbf{Image 6 Prompt:} Struggling man underwater, drowning.

    \textbf{Image 7 Prompt:} Wide shot, vast empty aircraft hangar interior, single figure in distance, harsh industrial lighting, dramatic shadows and highlights, sense of isolation and possibility, warm amber lighting contrasting cool narrative palette, cinematic scale, film texture.

    \textbf{Image 8 Prompt:} Top down shot inside boxing ring, warm arena lighting, golden hour color temperature, shallow focus on ring center, energetic and celebratory mood, young man is on the ring as a fighter, arms up, winning pose.

    \textbf{Image 9 Prompt:} Surreal wide shot, cosmic wormhole vortex, swirling galaxies and light trails converging toward center, character's silhouette dissolving into infinite spiral, ethereal lighting transition from underwater blue to cosmic purples and golds, peaceful transcendent atmosphere, otherworldly beauty, seamless blend of realism and fantasy.

    \textbf{Image 10 Prompt:} A young man floating in the river, only head outside water, breathing mouth open.